---
title: "Assignment_3_template_1"
name: Arden Moser
output: html_document
---
\
*I was unable to download the Assignment 3 template so I had to start from scratch*
\
# Practice with R
## Excercise 1
```{r}
sum(2000,20000)
```

# Objects
## Excercise 2
```{r}
a <- 5
b <- 2:20
a
b
```
The first two lines assign variables: a was assigned with a value of 5, b was assigned with a vector of values between 2 and 20.  The last two lines simply print the contents of each variable.

## Excercise 3
```{r}
sum1 <- a + b
sum2 <- sum(a,b)
```
```sum()``` gives a different result than ```+```.  ```+``` adds a to each value in b, giving a vector of 19 elements.  ```sum()``` adds all values in b and a, giving the total as a single value.

## Excercise 4
```{r}
b[5] + b[10]
```
The sum of the 5th and 10th elements of b is 17.

## Excercise 5
```{r}
b[3] + b[8] + b[10]
```
The sum of the 3rd, 8th, and 10th elements of b is 24.

# 2 Dimensional Objects
## Excercise 6
When extracting from a 2-dimensional object, the **first number specifies rows** and the **second number specifies columns**.
\
\
```m[3,]``` extracts all elements in row 3.
\
\
To extract the 3rd, 4th, and 5th columns as one object, you must type ```m[,3:5]```.

## Excercise 7
```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
cbind(m,101:105)
```
```cbind()``` adds a new column to the right side of the table.  The first dimension specifies the data table, *m* in this case.  The second dimension specifics the contents of the new column, which are values between 101 and 105 in this case.
